Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-09-17 WSSSPE4_report/WSSSPE4_report.tex
minor changes, adding papers section

The Fourth Workshop on Sustainable Software for Science: Practice and Experiences
(WSSSPE4)\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe4/}} was
held on 12--14 September 2016 in Manchester, England, UK.
This location and date was selected so that WSSSPE4 immediately preceded the
First Research Software Engineers (RSE) Conference.
Previous events in the WSSSPE series include
WSSSPE1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1/}}~\cite{WSSSPE1-pre-report,WSSSPE1},
held in conjunction with SC13;
WSSSPE1.1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1-1/}}, a
focused workshop organized jointly with the SciPy
conference\footnote{\url{https://conference.scipy.org/scipy2014/participate/wssspe/}};
WSSSPE2\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe2/}}~\cite{WSSSPE2-pre-report,WSSSPE2},
held in conjunction with SC14;
WSSSPE2.1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe2-1/}}, a
focused workshop organized again jointly with
SciPy\footnote{\url{http://scipy2015.scipy.org/ehome/115969/286469/}};
and WSSSPE3\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe3/}}~\cite{WSSSPE3},
held in Boulder, Colorado, USA.
Note that the WSSSPE series changed its name from ``Workshop on Sustainable
Software for Science: Practice and Experiences'' to ``Working towards
Sustainable Software for Science: Practice and Experiences'' to better reflect
the movement towards a community in addition to the associated workshop series.\katznote{really?  I must have missed that.  I remember the first workshop as being `working towards' and then future workshops as being `workshop on'.}

@@

The CoC was introduced at the beginning of WSSSPE4, with the CoC subcommittee
and a general email address introduced for reporting concerns or incidents, or
asking questions.
\todo{mention any/lack of violations/reports?}

@@

@@

Intro and description
%
\begin{enumerate}
\item \textbf{Names: \emph{title}}.
Description

>>>>

The Fourth Workshop on Sustainable Software for Science: Practice and Experiences
(WSSSPE4)\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe4/}} was
held on 12--14 September 2016 in Manchester, England, UK.
This location and date was selected so that WSSSPE4 immediately preceded the
First Research Software Engineers (RSE) Conference.
Previous events in the WSSSPE series include
WSSSPE1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1/}}~\cite{WSSSPE1-pre-report,WSSSPE1},
held in conjunction with SC13;
WSSSPE1.1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1-1/}}, a
focused workshop organized jointly with the SciPy
conference\footnote{\url{https://conference.scipy.org/scipy2014/participate/wssspe/}};
WSSSPE2\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe2/}}~\cite{WSSSPE2-pre-report,WSSSPE2},
held in conjunction with SC14;
WSSSPE2.1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe2-1/}}, a
focused workshop organized again jointly with
SciPy\footnote{\url{http://scipy2015.scipy.org/ehome/115969/286469/}};
and WSSSPE3\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe3/}}~\cite{WSSSPE3},
held in Boulder, Colorado, USA.
Note that the first WSSSPE workshop was named
``Working towards
Sustainable Software for Science: Practice and Experiences,'' which remains the meaning
of the WSSSPE group, but the workshops after that were named 
``Workshop on Sustainable
Software for Science: Practice and Experiences.'' Together these reflect
that WSSSPE is both a community in addition to a set of associated workshops.

@@

The CoC was introduced at the beginning of WSSSPE4, with the CoC subcommittee
and a general email address introduced for reporting concerns or incidents, or
asking questions.  There was one concern mentioned to the CoC subcommittee
after the first 1/2 day,
regarding how part of the workshop was being run, and we changed the workshop
to address this.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Papers and demos} \label{sec:papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Intro and description \katznote{not sure enum is right here}
%
\begin{enumerate}
\item \textbf{Names: \emph{title}}.
Description

@@

Intro and description \katznote{not sure enum is right here}
%
\begin{enumerate}
\item \textbf{Names: \emph{title}}.
Description
